### 2021-07-14 chapters/rq2/1_experiment_design.tex
minor typo
Updates from Overleaf

\subsubsection{Self organizing map, C-means and \acrlong{fcm}}
\label{ch:topThreeModels}
The \acrfull{som}, C-means and \acrfull{fcm} models are all models that would fit our purpose. 
To choose between these models we will look at the performance of each model.
Mingoti et al., compared the performance of these three models \cite{Mingoti2006ComparingAlgorithms}.
They did a Monte Carlo simulation where the cluster sizes and amount of random numbers in the data set varied each simulation\cite{Mingoti2006ComparingAlgorithms}.
Other variables such as cluster boundaries and overlap were also controlled in the experiment.
They observe that the C-means and \acrlong{fcm} had good performance for non overlapping situations\cite{Mingoti2006ComparingAlgorithms}.
The best results for average recovery and internal dispersion rates were found for \acrlong{fcm} which was very stable in all situations achieving recovery averages over 90\%\cite{Mingoti2006ComparingAlgorithms}
The C-means method was very affected by the presence of a large amount of outliers.
They conclude that the \acrshort{som} did not perform well in many cases being very affected by the amount of variables and clusters even for the non overlapping cases\cite{Mingoti2006ComparingAlgorithms}.
They also conclude that their results partially overlap with other research in the same domain.
\newline
Based on these results we can conclude that the \acrshort{fcm} model has the best performance overall.
For this experiment we select the \acrshort{fcm} model.

\subsection{Training strategy}
\label{ch:training_strategy}
Our data set contains of mutants represented by their characteristics. 
The characteristics of the mutants are generated per project and have a project specific context.
The relations between the different mutants are also specific per project.
For example mutant with a mutator in a certain project can have a different effect on the source code and can give other results than a mutator in a different project.
To keep the relations and context we decided to train a separate model per project.
\newline
To validate the model we need to split our data set into a training set and a validation set.
Our total data set consists of approximately 1 million mutants generated over fourteen projects.
Research has shown that if the data set is big enough a ratio of 80/20 is sufficient\cite{Guyon1997ARatio}.
We will divide each source projects into training and validation groups to reflect the 80/20 ratio as best as possible.
Depending on the amount of mutants per project we might not achieve a perfect 80/20 ratio.
The division of the mutants will be done randomly. 
To make our results reproducible we will select a random division based on a generated seed.
The seed generated for each run will be included in the results and can be found in the Github repository\cite{rbasarat-repo}.

\subsection{Implementation of algorithm}
The research paper of the \acrshort{fcm} algorithm is referenced in the survey paper of Du et al\cite{Du2010Clustering:Approach}.
The \acrshort{fcm} algorithm is developed by Bezdek et al.\cite{Bezdek1984FCM:Algorithm}.
Based on their research an implementation can be developed.
There are existing libraries that contain the implementation of the \acrshort{fcm} algorithm.
Developing our own version of the \acrshort{fcm} algorithm is out of scope for this research.
For this reason we choose to use a library that implements the \acrshort{fcm} algorithm.
The library we will use for this experiment is the \acrlong{fcm} implementation build by Dias et al.\cite{dias2019fuzzy}.
The theory developed by Bezdek et al., is implemented in this library.
The library has been used in other research\cite{DeAlmeidaNeto2020, Kopf2019, Nwadiugwu2020} and is actively maintained.

\subsection{Algorithm parameters}
The \acrshort{fcm} algorithm has to initialize the centroids of the clusters.
Our selected library does this based on a random number.
It also allows us to control this random number.
To make the initialization of the centroid reproducible and deterministic we will use a generated seed.
The seed generated is included in the Github repository\cite{rbasarat-repo}.
\newline
Bezdek et al., also researched cluster validity for the \acrshort{fcm} model\cite{Bezdek1995OnModel}.
They researched what effect which parameters have on the validity of the clusters.
They specifically analyzed the role of weighting exponent \textit{m}(fuzziness parameter).
They concluded that the best choice for \textit{m} is probably in the interval [1.5, 2.5], whose mean and midpoint is \textit{m}=2.
Wu proposed a new guideline for selecting parameter \textit{m}\cite{Wu2012}.
His point of view was that a large \textit{m} value will make the \acrlong{fcm} more robust to noise and outliers.
He suggests implementing \acrlong{fcm} with \textit{m}=[1.5, 4].
When the data set contains noise and outliers, the fuzzifier\textit{m}=4 is recommended in a theoretical upper bound case.
Since our data set does not contain noise and outliers we choose to select the midpoint concluded in the research of Bezdek et al.\cite{Bezdek1995OnModel}.
The value of \textit{m} in this experiment is 2.
\newline
Finding the correct amount of clusters has been an ongoing problem for clustering algorithms\cite{Du2010Clustering:Approach}.
Fortunately there are some techniques available to estimate the number of clusters.
During model selection we discussed the mountain and subtractive models. 
These models are designed to estimate the number of clusters in a data set.
The subtractive clustering model is specifically designed to approximate the number of clusters for fuzzy system models\cite{Chiu1994FuzzyEstimation}.
It approximates the centroids and amount of the clusters based on the data points in the data set\cite{Chiu1994FuzzyEstimation}.
We will select and implement the subtractive clustering model to estimate the number of clusters.
We can use this number for the number of clusters parameter in the \acrshort{fcm} algorithm.

>>>>

\subsubsection{Self organizing map, C-means and \acrlong{fcm}}
\label{ch:topThreeModels}
The \acrfull{som}, C-means and \acrfull{fcm} models are all models that would fit our purpose. 
To choose between these models we will look at the performance of each model.
Mingoti et al., compared the performance of these three models \cite{Mingoti2006ComparingAlgorithms}.
They did a Monte Carlo simulation where the cluster sizes and amount of random numbers in the data set varied each simulation\cite{Mingoti2006ComparingAlgorithms}.
Other variables such as cluster boundaries and overlap were also controlled variables in the experiment.
They observe that the C-means and \acrlong{fcm} had good performance for non overlapping situations\cite{Mingoti2006ComparingAlgorithms}.
The best results for average recovery and internal dispersion rates were found for \acrlong{fcm} which was very stable in all situations achieving recovery averages over 90\%\cite{Mingoti2006ComparingAlgorithms}
The C-means method was affected by the presence of a large amount of outliers.
They conclude that the \acrshort{som} did not perform well in many cases being affected by the amount of variables and clusters even for the non overlapping cases\cite{Mingoti2006ComparingAlgorithms}.
They also observe  that their results partially overlap with other research in the same domain.
\newline
Based the conclusions made by Mingoti et al., we can conclude that the \acrshort{fcm} model has the best performance overall.
Thus for this experiment we select the \acrshort{fcm} model.

\subsection{Training strategy}
\label{ch:training_strategy}
Our data set contains of mutants represented by their characteristics. 
The characteristics of the mutants are generated per project and have a project specific context.
The relations between the mutants are scoped to their own project. 
In other words if a specific mutant has a relation to another mutant in the same project, this relation may not exist between the same mutant and a mutant from a different project.
For example, a mutant with a mutator in a certain project can have a different effect on the source code and can give other results than a mutator in a different project.
To keep the relations and context we decided to train a separate model per project.
\newline
To validate the model we need to split our data set into a training set and a validation set.
Our total data set consists of approximately 1 million mutants generated over fourteen projects.
Research has shown that if the data set is big enough a ratio of 80/20 is sufficient\cite{Guyon1997ARatio}.
We will divide each source projects into training and validation groups to reflect the 80/20 ratio as best as possible.
Depending on the amount of mutants per project we might not achieve a perfect 80/20 ratio.
The division of the mutants will be done randomly. 
To make our results reproducible we will select a random division based on a generated seed.
The seeds generated for each run will be included in the results and can be found in the Github repository\cite{rbasarat-repo}.

\subsection{Implementation of algorithm}
The research paper of the \acrshort{fcm} algorithm is referenced in the survey of Du et al\cite{Du2010Clustering:Approach}.
The \acrshort{fcm} algorithm is developed by Bezdek et al.\cite{Bezdek1984FCM:Algorithm}.
Based on their research an implementation can be developed.
There are existing libraries that contain the implementation of the \acrshort{fcm} algorithm.
Developing our own version of the \acrshort{fcm} algorithm would be valuable if we want to make adjustments to the algorithm itself.
For this experiment we do not require to make adjustments to the \acrshort{fcm} algorithm.
Therefore we choose to use a library that implements the \acrshort{fcm} algorithm.
The library we will use for this experiment is the \acrlong{fcm} implementation build by Dias et al.\cite{dias2019fuzzy}.
The theory developed by Bezdek et al., is implemented in this library.
The library is actively maintained and has been used before in other research\cite{DeAlmeidaNeto2020, Kopf2019, Nwadiugwu2020}.

\subsection{Algorithm parameters}
The \acrshort{fcm} algorithm has to initialize the centroids of the clusters.
The library we selected does this based on a random number.
It also allows us to control this random number.
To make the initialization of the centroid reproducible we will use the same generated seeds as in our first experiment.
The seeds generated are included in the Github repository\cite{rbasarat-repo}.
\newline
Bezdek et al., also researched cluster validity for the \acrshort{fcm} model\cite{Bezdek1995OnModel}.
They researched what effect which parameters have on the validity of the clusters.
They specifically analyzed the role of weighting exponent \textit{m}(fuzziness parameter).
They concluded that the best choice for \textit{m} is probably in the interval [1.5, 2.5], whose mean and midpoint is \textit{m}=2.
Wu proposed a new guideline for selecting parameter \textit{m}\cite{Wu2012}.
His point of view was that a large \textit{m} value will make the \acrlong{fcm} more robust to noise and outliers.
He suggests implementing \acrlong{fcm} with \textit{m}=[1.5, 4].
When the data set contains noise and outliers, the fuzzifier \textit{m}=4 is recommended in a theoretical upper bound case.
Since our data set does not contain noise and outliers we choose to select the midpoint concluded in the research of Bezdek et al.\cite{Bezdek1995OnModel}.
The value of \textit{m} in this experiment is 2.
\newline
Finding the correct amount of clusters has been an ongoing problem for clustering algorithms\cite{Du2010Clustering:Approach}.
Fortunately there are some techniques available to estimate the number of clusters.
During model selection we discussed the mountain and subtractive models. 
These models are designed to estimate the number of clusters in a data set.
The subtractive clustering model is specifically designed to approximate the number of clusters for fuzzy system models\cite{Chiu1994FuzzyEstimation}.
It approximates the centroids and amount of the clusters based on the data points in the data set\cite{Chiu1994FuzzyEstimation}.
We will select and implement the subtractive clustering model to estimate the number of clusters.
We can use this number for the number of clusters parameter in the \acrshort{fcm} algorithm.
